Efficient and Robust Boolean Operations on N Meshes Based on Hybrid Representations

### 2017-01-21 tex/class.tex
hello

\label{sec:classification}
%We traverse each face in the intersection-free meshes, and classify which one belongs to the final mesh. Classification is done by evaluating the label vector $\bm{\Lambda}$ of each face. The basic idea of our classification method is to utilize the space coherence of face label vectors to share the classification results among neighboring faces. Also, because we store the neighborhood information in the edges which intersect other meshes, the search space of point-in-polyhedron test is limited to only a few faces. It makes the label computation very fast. Finally, by using P-reps, our classification method is exact can deal with any degenerate cases.

We traverse each face of the primitives, and determine which belong to the final mesh. The faces are classified by evaluating their inclusion label vector. Our classification method utilizes the space coherence of the label vectors, and shares the classification results among neighboring faces. Because we store the neighboring faces in the edges where intersections occur, the label computation is very fast according to the orientation of these neighboring faces.

Intersection-free meshes facilitate this process by accelerating the label propagation. From adjacent faces $\bm{s}_1$ and $\bm{s}_2$, it is straightforward to determine whether $\bm{\Lambda}(\bm{s}_1)$ and $\bm{\Lambda}(\bm{s}_2)$ are different. The two label vectors are the same unless the shared edge $\bm{e}_{12}$ lies on the boundary of another mesh. In that cases, neighborhood information, say, $\bm{\mathcal{N}}(\bm{e}_{12}) = \{\mathcal{N}_k\}$, is stored on $\bm{e}_{12}$. Here we use $\bm{\mathcal{N}}$ to indicate that the edge may have more than one neighborhood (see \S\ref{sec:refine}). The neighborhood information indicates which components of the label vector differ between $\bm{s}_1$ and $\bm{s}_2$. If there is neighborhood information from mesh $M_x$, the $x^{th}$ labels $\lambda_x(\bm{s}_1)$ and $\lambda_x(\bm{s}_2)$ differ, and can be computed efficiently and exactly with respect to that neighborhood. We outline our classification method in Algorithm \ref{code:floodfill}.

%The space coherence of label vectors means neighboring faces may have the same label vector, or most components of label vectors. Therefore, we start from a seed face $\bm{s}_0$ with its label vector $\bm{\Lambda}(\bm{s}_0)$ known, and propagate to other faces in a flood-filling manner. The trace of label propagation is:

% The space coherence of label vectors means that neighboring faces may have the same label vector, or most of the components of the label vectors. Therefore, we start from a seed face $\bm{s}_0$ with a known label vector $\bm{\Lambda}(\bm{s}_0)$, and propagate the label to other faces in a flood-filling manner. The trace of the label propagation is:

% \begin{equation}
% \label{eq:trace}
% \bm{s}_0\to \bm{s}_1\to \bm{s}_2\to \bm{s}_3\to ...
% \end{equation}

%Intersection-free meshes facilitate this process by accelerating the label propagation. From adjacent faces s1 and s2, it is straightforward to determine whether

\begin{algorithm}[ht]
\caption{Fast Face Classification}
\label{code:floodfill}
\textbf{Input: } Intersection-free hybrid meshes, boolean function $f$

\textbf{Output: } Classification $f(\bm{\Lambda}(\bm{s}_i))$ for all faces $\bm{s}_i$

@@

\subsection{label Propagation}
\label{sec:propagation}

%Meshes consist of vertices, edges and faces. Classification is required to perform on the face level. However, polyhedron-in-out test is performed based on points. Gaps exist between the them. Conventionally, face barycenter is used to compute the label of the whole face. This is because in intersection-free meshes, face is classified as a whole, and every face inner point will have the same label as the face's. However, the computation of inner point coordinates requires geometry construction, which introduces errors without exact arithmetic. Therefore, we use the face (or subface) vertices instead, whose exact representations are known, for label computation.

Meshes consist of vertices, edges and faces. It is necessary to perform classification at the face level. However, polyhedron-in-out tests are performed on points, where gaps exist between them. Conventionally, the face barycenter is used to compute the label of the whole face because in intersection-free meshes, the face is classified as a whole, and every inner point of the face will have the same label as the whole face. However, the computation of inner point coordinates requires geometric constructions, which introduce errors unless exact arithmetic can be used. Therefore, we use the face (or subface) vertices instead, the exact representations of which are known, for label computation.

>>>>

\label{sec:classification}

We traverse each face of the primitives, and determine which belong to the final mesh. The faces are classified by evaluating their inclusion label vector. Our classification method utilizes the space coherence of the label vectors, and shares the classification results among neighboring faces. Because we store the neighboring faces in the edges where intersections occur, the difference of labels between adjacent faces are computed according to the BSP constructed with these neighboring faces. For arbitrary adjacent faces $\bm{s}_1$ and $\bm{s}_2$, the label vectors $\bm{\Lambda}(\bm{s}_1)$ and $\bm{\Lambda}(\bm{s}_2)$ differ if their shared edge $\bm{e}_{12}$ lies on the surface of any other primitive.
In that cases, some neighboring faces should be stored on $\bm{e}_{12}$. The owner primitives of these neighboring faces indicate which labels differ. If there are neighboring faces from mesh $M_x$, the labels $\lambda_x(\bm{s}_1)$ and $\lambda_x(\bm{s}_2)$ differ. We outline our classification method in Algorithm \ref{code:floodfill}.

\begin{algorithm}[ht]
\caption{Fast Face Classification}
\label{code:floodfill}
\textbf{Input: } Tessellated primitives and boolean expression $f$

\textbf{Output: } Classification $f(\bm{\Lambda}(\bm{s}_i))$ of each face $\bm{s}_i$

@@

\subsection{Label Computation}
\label{sec:propagation}

In methods like \cite{feito2013fast,ogayar2015deferred}, the face barycenter is used to compute the inclusion label of the face. This is because the face can be classified as a whole, and all inner points of the face has the same label vector. In methods like \cite{zhou2016mesh}, points inside the cell is used for label computation, and the face labels are decided by the labels of the two sides of the face. However, all these methods require to construct new vertices, whose coordinates require rational numbers to store, or round-off errors may be introduced. Incorrect label computation may occur because of such errors. To avoid this, we use the vertices instead, the exact coordinates of which are known.

### 2017-01-21 tex/exp.tex
hello

\iffalse

\subsection{Implementation}

\label{sec:individual}

Feito et. al. \cite{feito2013fast} had noticed that intersection neighborhood can be used for fast classification of faces around that intersection. According to their method, faces adjacent to intersection have neighbors from other primitive(\bm{s}) that define the position and orientation for each other, by which the indicators are determined. However, Feito et. al. did not give detail description of how to implement an exact and robust classification. Their implementation of using vertex coordinates might misclassify faces by numeric errors and fail in degenerate cases. Because geometry connectivity is used, local misclassification can be spread to the neighborhoods, leading to errors in wide ranges.

We develop an classification method that is unconditionally robust and exact based on the idea of using intersection neighborhood information. The neighborhood information is stored in the context component of I-reps during previous stages . In the following, we discuss the conditions that the face to be classified is a triangle. If the face is not a triangle, we select a triangle slice of the face instead, as the whole face is guaranteed to be classified together. Note that the chosen slice should contain the edge where the I-reps lie, by which we compute the new indicators.

Given a face $t_i$ to be classified and an I-rep $\boldsymbol\Gamma$ of intersection on one of $t_i$'s edge, we denote the three corners it as $\bm{v}_{b*}^{0}(t_i), \bm{v}_{b*}^{1}(t_i), \bm{v}_b^2(t_i),$ where the subscript $*$ means the vertices are on the edge where $\boldsymbol\Gamma$ lies. We also denote the context component of $\boldsymbol\Gamma$ as $C_{P_h \backslash P_j}$, meaning $t_i$ is from primitive $M_j$ and intersects primitive $M_h$. From previous discussion (section \ref{sec:ir}){\color{red}{may be more than one}}, we know there are two types of intersection context---face neighborhood and edge neighborhood. In both conditions, the one or two faces involving in the context split the space into two in and out space by its (their) orientation(\bm{s}). We will see that under such division (denoted as $\boldsymbol{D}(C_{P_h \backslash P_j})$), we can compute $\lambda(t_i, P_j)$ exactly.

Since the faces involving in $C_{P_h \backslash P_j}$ is part of primitive $M_j$, the space division $\boldsymbol{D}(C_{P_h \backslash P_j})$ is homogeneous with the space division by $M_j$ in neighborhood of $\bm{\mathcal{I}}$. The basic idea is to choose one point $\bm{v}_x(t_i)$ on $t_i$ close enough to $\bm{\mathcal{I}}$ to compute $\lambda(\bm{v}_x(t_i), P_j)$, and then compute $\lambda(t_i, P_j)$ accordingly. However, the problem is that we cannot find such a $\bm{v}_x(t_i)$ that can be represented exactly, which means robust classification cannot be performed. Fortunately, we observe that we can choose $\bm{v}_b^2(t_i)$, which is not so close to $\bm{\mathcal{I}}$ instead. To illustrate, assume there is another point $\bm{v}_{x'}(t_i)$ inside of $t_i$ that is very close to $\bm{v}_b^2(t_i)$ ({\color{red}{Fig. x}}). Because all inner points of $t_i$ have the same indicator, $\lambda(\bm{v}_x(t_i), P_j) = \lambda(\bm{v}_{x'}(t_i), P_j)$. On the other hand, we find that $\lambda(\bm{v}_{x'}(t_i), P_j)$ and $\lambda(\bm{v}_b^2(t_i), P_j)$ are always equal under division $\boldsymbol{D}(C_{P_h \backslash P_j})$ ({\color{red}{see Appendix \ref{app:profind}}}). Therefore, $\lambda(\bm{v}_b^2(t_i), P_j)$ is equal to $\lambda(\bm{v}_x(t_i), P_j)$ under $\boldsymbol{D}(C_{P_h \backslash P_j})$, and are coherent with $\lambda(t_i, P_j)$ under the division of whole primitive $M_j$. One additional thing is that when $\lambda(\bm{v}_2(t_i), P_j)=on$, then $\lambda(t_i, P_j)$ can be either $same$ or $oppo$. The normal orientation test have to be performed to eliminate such ambiguity.

\fi

@@

\begin{figure}[t]
\centering
\includegraphics[width=3in]{dual}
\caption{a) There is ambiguity as to the orientation of the loop in this tess-graph. b) When there is more than one connected component in a tess-graph, auxiliary intersections (yellow line) are used to connect the components.}
%a) There is ambiguity with the orientation of the loop in a tess-graph. b) When there are more than one connected component in tess-graph, we use auxiliary intersection (yellow line) to connect the two component. }
\label{fig:dual}
\end{figure}

@@

%We noticed that for CSGs that contains a lot of meshes within small area (e.g., Table. \ref{tab:performance}, \emph{T1}), the performance of our method is poor. This is because in such situations, our method computes many intersections that will not appear as edges in the final mesh, which leads to unnecessary tessellation. Optimization may be explored to avoid such problem.

%The input of our method is limited to regular set meshes. However, recent works claim that the piece-wise wind number (PWN) are more powerful to identify the inside and outside of meshes \cite{zhou2016mesh}.  By using PWN, the input requirements can be extended to so-called PWN meshes that allow topology deficiencies such as self-intersection and multi-component. It would be interesting to extend our method to PWN method in the future.

We found that performance of our method was poor for CSGs that contained a lot of meshes within a small area (Table. \ref{tab:performance}, \emph{T1}). In these cases, our method computes many intersections that will not appear as edges in the final mesh, leading to unnecessary tessellation. Optimization may be explored to minimize this problem.

The application of our method is limited to regular set meshes. However, recent reports have proposed that the piece-wise wind number (PWN) is a more powerful method to identify the insides and outsides of meshes \cite{zhou2016mesh}. The input requirements of our method may be extended to PWN meshes, that allow topological deficiencies, such as self-intersection and multi-components. We believe that this would be an interesting and valuable extension of our work.

@@

%In this paper, we proposed a novel method to evaluate CSG models. It is able to efficiently perform unconditionally robust non-incremental boolean operations. The key idea of our approach is to embed P-reps information into B-reps. The P-reps give us the chance to strictly follow the principle of no geometry construction to avoid numerical errors. And the B-reps offer fast neighborhood query to accelerate the processing. Experiments have verified the performance of our method is competitive with state-of-the-art non-robust methods while guarantee robustness.

In this paper, we propose a novel method to evaluate CSG models. This method can efficiently perform unconditionally robust non-incremental boolean operations. The novel component of our approach is to embed P-rep information into B-reps. P-reps allow us to strictly follow the principle of no geometry construction to avoid numerical errors. The use of B-reps enables fast neighborhood queries to reduce the computation time. The experimental results show that the performance of our method is competitive with state-of-the-art non-robust methods, while guaranteeing robustness.

>>>>

@@

\begin{figure}[t]
\centering
\includegraphics[width=3in]{dual}
\caption{a) There is ambiguity as to the orientation of the loop in this tess-graph. b) When there is more than one connected component in a tess-graph, auxiliary intersections (yellow line) are used to connect the components.}
\label{fig:dual}
\end{figure}

@@

We found that performance of our method was poor for CSGs that contained a lot of meshes within a small area (Table. \ref{tab:performance}, \emph{T1}). In these cases, our method computes many intersections that will not appear as edges in the final mesh, leading to unnecessary tessellation. Optimization may be explored to alleviate this problem.

The inputs of our method are limited to solids. However, recent reports have proposed that the piece-wise wind number (PWN) is a more powerful method to identify the insides and outsides of meshes \cite{zhou2016mesh}. The input requirements of our method may be extended to PWN meshes, that allow self-intersection. We believe that this would be an interesting and valuable extension of our work.

@@

In this paper, we propose a novel boolean method. Our method can efficiently perform variadic boolean operations, and is robust with solid inputs. The novel component of our approach is to combine P-reps with V-reps. P-reps allow us to strictly follow the principle of no geometry construction to avoid numerical errors ,and the V-reps enables coarse tests and fast neighborhood queries to reduce the need of slow plane-based computation. The experimental results show that the performance of our method is competitive with state-of-the-art non-robust methods, while guaranteeing robustness under consistent inputs.

### 2017-01-21 tex/inter.tex
hello

When a triangle intersects with the edge of other triangle, the generated intersection is referred as \emph{edge intersection}. The neighboring faces of the intersection is the set of all the faces that shared the edge rather than a single face. For example, in Fig. \ref{fig:twin}a, the neighboring faces of the intersection on $t_1$ are $t_2$ and $t^*_2$.

An edge intersection will be repeatedly detected. For example, in Fig. \ref{fig:twin}a, the same intersection on $t_1$ will be detected twice, because $t_1$ intersects both $t_2$ and $t_2^*$ at the same line segment. We solve this duplication in tessellation stage (see \S\ref{sec:tessellation}). We regard $t_2$ and $t_2^*$ as \emph{companion} triangles, because they are the neighboring faces of the same edge intersection. This concept will be referred to again in the discussion of coplanar cases.

>>>>

When a triangle intersects with the edge of other triangle, the generated intersection is referred as \emph{edge intersection}. The neighboring faces of the intersection is the set of all the faces that shared the edge rather than a single face. For example, in Fig. \ref{fig:twin}a, the neighboring faces of the intersection on $t_1$ are $t_2$ and $t^*_2$. The same intersection on $t_1$ will be detected twice, because $t_1$ intersects both $t_2$ and $t_2^*$ at the same line segment. In fact, edge intersections are often detected for multiple times. We solve this duplication in tessellation stage (see \S\ref{sec:tessellation}). We regard $t_2$ and $t_2^*$ as \emph{companion} triangles, because they are the neighboring faces of the same edge intersection. This concept will be referred to again in the discussion of coplanar cases.

### 2017-01-21 tex/overview.tex
hello

Most of the existing boolean methods follow such two-step paradigm---intersection computation and face classification, as does our method. Non-robustness comes from three stages of such boolean methods. 1) The intersection between faces may not be exactly computed. 2) Face tessellation produces inconsistent topology. 3) The computation of the inclusion labels is not consistent with the location of the faces (see Fig. \ref{fig:falseclass}). These problems all come from the numerical errors during geometric computation. Therefore, if these three stages can be performed in exact ways, boolean evaluations are robust.

\begin{figure}[t]
\centering
\includegraphics[width=2.2in]{boolean-01}
\caption{In this 2D view, face $\bm{s}$ (the red line segment) of mesh $M_2$ is on the surface of mesh $M_1$. However, because the face barycenter $\bm{v}_{c(\bm{s})}$ is used to compute the labels, the coordinates of which contain round-off errors, the point could be moved to $\bm{v'}_{c(\bm{s})}$. Thus, $\bm{s}$ may be falsely classified as being outside of $M_1$.}
\label{fig:falseclass}
\end{figure}

>>>>

Most of the existing boolean methods follow such two-step paradigm---intersection computation and face classification, as does our method. Non-robustness comes from three stages of such boolean methods. 1) The intersection between faces may not be exactly computed. 2) Face tessellation produces inconsistent topology. 3) The computation of the inclusion labels is not consistent with the location of the faces. These problems all come from the numerical errors during geometric computation. Therefore, if these three stages can be performed in exact ways, boolean evaluations are robust.

% \begin{figure}[t]
% \centering
% \includegraphics[width=2.2in]{boolean-01}
% \caption{In this 2D view, face $\bm{s}$ (the red line segment) of mesh $M_2$ is on the surface of mesh $M_1$. However, because the face barycenter $\bm{v}_{c(\bm{s})}$ is used to compute the labels, the coordinates of which contain round-off errors, the point could be moved to $\bm{v'}_{c(\bm{s})}$. Thus, $\bm{s}$ may be falsely classified as being outside of $M_1$.}
% \label{fig:falseclass}
% \end{figure}
